The Impact of Educational Expenses of New Coders

### 2021-04-14 outputs/paper/paper.Rmd
Add the  package

library(tidyverse)
library(dplyr)
library(stargazer)
library(psych)
# install.packages("PerformanceAnalytics")
library(PerformanceAnalytics)
# install.packages("QuantPsyc")
library(QuantPsyc)
library(car)
```

@@

#### Get data ####
dfNewCoders <- 
  readr::read_csv("../../inputs/data/clean_new-coders.csv")

>>>>

library(tidyverse)
library(dplyr)
library(stargazer)
library(psych)
# install.packages("here")
library(here)
# install.packages("PerformanceAnalytics")
library(PerformanceAnalytics)
# install.packages("QuantPsyc")
library(QuantPsyc)
library(car)
```

@@

#### Get data ####
dfNewCoders <- 
  readr::read_csv(here::here("inputs/data/clean_new-coders.csv"))
